### 2016-12-28 Chapters/experiments.tex
Change titlepage (new format) and write Suppinfo S5 about strains

\begin{figure}[tb]
\centering
\includegraphics[scale=1]{./Fig/experiment_schema.eps}
\caption{
\textbf{Schematic outline of the upshift experiment.}
The goal is to measure the fluorescence and length/area of \textit{E. coli} \textit{rpsB-gfp} cells during an acetate-to-glucose upshift.
We use M9 minimal medium supplemented with 0.2\% of acetate or glucose (see Material and Methods~\ref{sec:growth_condition}).
A preculture was started from glycerol stock for 2.5 days on 0.2\% acetate in batch condition (shake flask).
The day of the experiment, the cells were injected into the mothermachine and fed by a constant flow of fresh 0.2\% acetate medium (see Material and Methods~\ref{sec:microflu}).
Fluorescence and phase contrast images were taken every 5 minutes.
After 20~h, the feeding media was switched to 0.2\% glucose and maintained for 20~h while continuing image acquisition.
Time 0 corresponds to the moment of the acetate-glucose upshift.
}
\label{fig:experiment_schema}
\end{figure}

@@

(Plan not complete)

\subsection{Strain construction}

Primers used for gibson assembly

\subsection{Strain validation using growth in microplate reader}

@@

\subsection{Microscopy analysis}

Show the complete analysis for 5 cells.

\subsubsection*{Category of cells}

@@

>>>>

\begin{figure}[tb]
\centering
\includegraphics[scale=1]{./Fig/experiment_schema}
\caption{
\textbf{Schematic outline of the upshift experiment.}
The goal is to measure the fluorescence and length/area of \textit{E. coli} \textit{rpsB-gfp} cells during an acetate-to-glucose upshift.
We use M9 minimal medium supplemented with 0.2\% of acetate or glucose (see Material and Methods~\ref{sec:growth_condition}).
A preculture was started from glycerol stock for 2.5 days on 0.2\% acetate in batch condition (shake flask).
The day of the experiment, the cells were injected into the mothermachine and fed by a constant flow of fresh 0.2\% acetate medium (see Material and Methods~\ref{sec:microflu}).
Fluorescence and phase contrast images were taken every 5 minutes.
After 20~h, the feeding media was switched to 0.2\% glucose and maintained for 20~h while continuing image acquisition.
Time 0 corresponds to the moment of the acetate-glucose upshift.
}
\label{fig:experiment_schema}
\end{figure}

@@

\subsection{S5 Text -- Strain construction}
\manuallabel{S5_Text}{S5~Text}

\subsubsection{Exhaustive list of the primers used...}

\paragraph{...for the \textit{gfpmut2} amplification.}

\begin{itemize}
\item[] \includegraphics[scale=1]{Fig/gfpmut2_L.png} \seqsplit{GTTCTCAGGATCTGGCTTCCCAGGCGGAAGAAAGCTTCGTAGAAGCTGAGCAGGAAAGGCGACAGGAGAGTAAAGGAGAAGAACTTTTCACTG}
(Length: 93)
\item[] \includegraphics[scale=1]{Fig/gfpmut2_R.png} \seqsplit{TGATGTTCTGGGGAATATAATTATTTGTATAGTTCATCCATGCC} (Length: 44)
\end{itemize}

\textbf{Rem.} The 50 first bases of the forward primer are supposed to anneal with the end of the \textit{rpsB} gene.
The 20 last bases of the reverse primer are supposed to anneal with the ccdB-end of the \textit{kan-P\textsubscript{BAD}-ccdB} cassette.

\paragraph{...for the \textit{mCherry} amplification}

\begin{itemize}
\item[] \includegraphics[scale=1]{Fig/mCherry_L.png} \seqsplit{GTTCTCAGGATCTGGCTTCCCAGGCGGAAGAAAGCTTCGTAGAAGCTGAGCAGGAAAGGCGACAGGAGACTAGCAAAAGATCCAAGGG}
(Length: 88)
\item[] \includegraphics[scale=1]{Fig/mCherry_R.png} \seqsplit{TGATGTTCTGGGGAATATAATTATTTGTACAGCTCATCCATG} (Length: 42)
\end{itemize}

\textbf{Rem.} The 50 first bases of the forward primer are supposed to anneal with the end of the \textit{rpsB} gene.
The 20 last bases of the reverse primer are supposed to anneal with the ccdB-end of the \textit{kan-P\textsubscript{BAD}-ccdB} cassette.

\paragraph{...for the cassette amplification}

\begin{itemize}
\item[] \includegraphics[scale=1]{Fig/cassette_L} \seqsplit{TGGATGAACTATACAAATAATTATATTCCCCAGAACATCAGG}
(Length: 42, used to assemble with gfp)
\item[] \includegraphics[scale=1]{Fig/cassette_L} \seqsplit{TGGATGAGCTGTACAAATAATTATATTCCCCAGAACATCAG}
(Length: 41, used to assemble with mCherry)
\item[] \includegraphics[scale=1]{Fig/cassette_R} \seqsplit{GAGCTTGCCGCCTTTCTGCAACTCGAACTATTTTGGGGGAGTTATCAAGCTTAGAAGAACTCGTCAAGAAGG}
(Length: 72, used for both)
\end{itemize}

\textbf{Rem.} The 20 first bases of the first forward primer are supposed to anneal with the end of the \textit{gfpmut2} gene.
The 20 first bases of the second forward primer are supposed to anneal with the end of the \textit{mCherry} gene.
The 50 last bases of the reverse primer are supposed to anneal with the region after \textit{rpsB} on the \textit{E.~coli} BW25113 chromosome.

\paragraph{...for the whole insert amplification}

\begin{itemize}
\item[] \includegraphics[scale=1]{Fig/overlap_L} \seqsplit{GTTCTCAGGATCTGGCTTCCCAGG}
(Length: 24)
\item[] \includegraphics[scale=1]{Fig/overlap_R} \seqsplit{GAGCTTGCCGCCTTTCTGCA} (Length: 20)
\end{itemize}

\paragraph{...for the cassette elimination}

\begin{itemize}
\item[\textbf{\textit{rpsB-gfpmut2}}] \seqsplit{TTGTAACAGCTGCTGGGATTACACATGGCATGGATGAACTATACAAATAAGCTTGATAACTCCCCCAAAATAGTTCGAGTTGCAGAAAGGCGGCAAGCTC}
(Length: 100)
\item[\textbf{\textit{rpsB-mCherry}}] \seqsplit{GCGCGGAGGGTCGTCATTCTACCGGTGGCATGGATGAGCTGTACAAATAAGCTTGATAACTCCCCCAAAATAGTTCGAGTTGCAGAAAGGCGGCAAGCTC}
(Length: 100)
\end{itemize}

\paragraph{...for the sequencing of the final strain}

\begin{itemize}
\item[] \includegraphics[scale=1]{Fig/sequencing_L} \seqsplit{CGTCTGAAAGACCTGGAAAC}
(Length: 20)
\item[] \includegraphics[scale=1]{Fig/sequencing_R} \seqsplit{AAACGTGTACTACCTGGTCTATAAGG} (Length: 26)
\end{itemize}

\subsubsection{Full sequence of the inserts}

The following pages contain the full sequences of the \textit{gfpmut2-cassette} and \textit{mCherry-cassette} constructions, inserted on the \textit{E.~coli} BW25113 chromosome at the region after the \textit{rpsB} gene.
The primers annealing positions are indicated using the same color code as in the description of the primers above.
The primers reported in the original publication of Bakshi \textit{et al}~\cite{bakshi_superresolution_2012} are indicated for information.

\includepdf[pages={1-7}]{./Fig/gfp-mut2-cassette-after-rpsB-gene-sequence.pdf}
\includepdf[pages={1-6}]{./Fig/mcherry-cassette-after-rpsB-gene-sequence.pdf}

\subsubsection{Sequencing of the final strains}

The strains were constructed using the protocol described in Material and Methods~\ref{sec:methods_strain}.
Regions at the end of the \textit{rpsB} gene were amplified, and sent for sequencing.
Alignments of the results showed they exhibit the expected sequences.
The raw results of the sequencing are reproduced below.

\paragraph{Final sequences of the \textit{rpsB-gfpmut2} strain (region after \textit{rpsB})}

\begin{small}
\begin{itemize}
\item[] \includegraphics[scale=1]{Fig/sequencing_L} \seqsplit{AGAAAGAAGCGCTGTATGCGCACTCGTGAGCTGGAGAAACTGGAAAACAGCCTGGGCGGTATCAAAGACATGGGCGGTCTGCCGGACGCTCTGTTTGTAATCGATGCTGACCACGAACACATTGCTATCAAAGAAGCAAACAACCTGGGTATTCCGGTATTTGCTATCGTTGATACCAACTCTGATCCGGACGGTGTTGACTTCGTTATCCCGGGTAACGACGACGCAATCCGTGCTGTGACCCTGTACCTGGGCGCTGTTGCTGCAACCGTACGTGAAGGCCGTTCTCAGGATCTGGCTTCCCAGGCGGAAGAAAGCTTCGTAGAAGCTGAGCAGGAAAGGCGACAGGAGCGTAAAGGAGAAGAACTTTTCACTGGAGTTGTTCCAATTCTTGTTGAATTAGATGGTGATGTTAATGGGCACAAATTTTCTGTCAGTGGAGAGGGTGAAGGTGATGCAACATA}
\item[] \includegraphics[scale=1]{Fig/sequencing_R} \seqsplit{CGCCGCAGATGCGTTATCTTCGCTCGCTCATCCCGGTCACTTACTGATGTAAGCTCCCGGGAATTCTCGAGCTTGCCGCCTTTCTGCAACTCGAACTATTTTGGGGGAGTTATCAAGCTTATTTGTATAGTTCATCCATGCCATGTGTAATCCCAGCAGCTGTTACAAACTCAAGAAGGACCATGTGGTCTCTCTTTTCGTTGGGATCTTTCGAAAGGGCAGATTGTGTGGACAGGTAATGGTTGTCTGGTAAAAGGACAGGGCCATCGCCAATTGGAGTATTTTGTTGATAATGGTCTGCTAGTTGAACGCTTCCATCTTCAATGTTGTGTCTAATTTTGAAGTTAACTTTGATTCCATTCTTTTGTTTGTCTGCCATGATGTATACATTGTGTGAGTTATAGTTGTATTCCAATTTGTGTCCAAGAATGTTTCCATCTTCTTTAAAATCAATACCTTTTAACTCGATTCTATTAACAAGGGTATCACCTTCAAACTTGACTTCAGCACGTGTCTTGTAGTTCCCGTCATCTTTGAAAAATATAGTTCTTTCCTGTACATAAACCTTCGGGCATGGCACTCTTGAAAAAGTCATGCTGTTTCATATGATCTGGGTATCTCGCAAAGCATTGAAGACCATACGCGAAAAGTAGTGACAAGTGTTGGCCATGGAACAGGTAGTTTTCCAGTAGTGCAAATAAATTTAAGGGTAAAGTTTTCCGTATGTTGCATCACCTTCACCCTCTCCACTGACAGAAAAATTTGTGCCCATTTAACATCACCATCTAATTCAACAAGAATTGGAAACAACTCCAGTGAAAGT} 
\end{itemize}
\end{small}

\newpage
\paragraph{Final sequences of the \textit{rpsB-mCherry} strain (region after \textit{rpsB})}

\begin{small}
\begin{itemize}
\item[] \includegraphics[scale=1]{Fig/sequencing_L}
\seqsplit{TTTCGACAGCTGACCAAGAAGAAGCGCTGATGCGCACTCGTGAGCTGGAGAAACTGGAAA
ACAGCCTGGGCGGTATCAAAGACATGGGCGGTCTGCCGGACGCTCTGTTTGTAATCGATG
CTGACCACGAACACATTGCTATCAAAGAAGCAAACAACCTGGGTATTCCGGTATTTGCTA
TCGTTGATACCAACTCTGATCCGGACGGTGTTGACTTCGTTATCCCGGGTAACGACGACG
CAATCCGTGCTGTGACCCTGTACCTGGGCGCTGTTGCTGCAACCGTACGTGAAGGCCGTT
CTCAGGATCTGGCTTCCCAGGCGGAAGAAAGCTTCGTAGAAGCTGAGCAGGAAAGGCGAC
AGGAGACTAGCAAAAGATCCAAGGGCGAGGAGGATAACATGGCTATCATTAAAGAGTTCA
TGCGCTTCAAAGTTCACATGGAGGGTTCTGTTAACGGTCACGAGTTCGAGATCGAAGGCG
AAGGCGAGGGCCGTCCGTATGAAGGCACCCAGACCGCCAAACTGAAAGTGACTAAAGGCG
GCCCGCTGCCTTTTGCGTGGGACATCCTGAGCCCGCAATTTATGTACGGTTCTAAAGCGT
ATGTTAAACACCCAGCGGATATCCCGGACTATCTGAAGCTGTCTTTTCCGGAAGGTTTCA
AGTGGGAACGCGTAATGAATTTTGAAGATGGTGGTGTCGTGACCGTCACTCAGGACTCCT
CCCTGCAAGATGGCGAGTTCATCTATAAAGTTAAACTGCGTGGTACTAATTTTCCATCTG
ATGGCCCGGTGATGCAGAAAAAGACGATGGGTTGGGAGGCGTCTAGCGAACGCATGTATC
CGGAAGATGGTGCGCTGAAAGGCGAAATTAAACAGCGCCTGAAACTGAAAGATGGCGG}
\item[] \includegraphics[scale=1]{Fig/sequencing_R}
\seqsplit{TTCGCGCCGCAGATGCGTTATCTTCGCTCGCTCATCCCGGTCACTTACTGATGTAAGCTC
CCGGGAATTCTCGAGCTTGCCGCCTTTCTGCAACTCGAACTATTTTGGGGGAGTTATCAA
GCTTATTTGTACAGCTCATCCATGCCACCGGTAGAATGACGACCCTCCGCGCGCTCATAT
TGCTCTACGATCGTATAATCTTCATTATGAGAGGTGATGTCCAGTTTAATATTCACATTG
TACGCGCCAGGCAGCTGCACAGGTTTCTTGGCTTTGTACGTGGTTTTCACTTCAGCGTCA
TAATGGCCGCCATCTTTCAGTTTCAGGCGCTGTTTAATTTCGCCTTTCAGCGCACCATCT
TCCGGATACATGCGTTCGCTAGACGCCTCCCAACCCATCGTCTTTTTCTGCATCACCGGG
CCATCAGATGGAAAATTAGTACCACGCAGTTTAACTTTATAGATGAACTCGCCATCTTGC
AGGGAGGAGTCCTGAGTGACGGTCACGACACCACCATCTTCAAAATTCATTACGCGTTCC
CACTTGAAACCTTCCGGAAAAGACAGCTTCAGATAGTCCGGGATATCCGCTGGGTGTTTA
ACATACGCTTTAGAACCGTACATAAATTGCGGGCTCAGGATGTCCCACGCAAAAGGCAGC
GGGCCGCCTTTAGTCACTTTCAGTTTGGCGGTCTGGGTGCCTTCATACGGACGGCCCTCG
CCTTCGCCTTCGATCTCGAACTCGTGACCGTTAACAGAACCCTCCATGTGAACTTTGAAG
CGCATGAACTCTTTAATGATAGCCATGTTATCCTCCTCGCCCTTGGAT} 
\end{itemize}
\end{small}

\subsection{S6 Text -- Strain validation}
\manuallabel{S6_Text}{S6~Text}

@@

\subsection{S7 Text -- Microscopy analysis}
\manuallabel{S7_Text}{S7~Text}

\subsubsection{Category of cells}

@@

\subsubsection{Noise estimation}

Blabla

\subsubsection{Complete analysis for 5 cells}

blabla

### 2016-12-28 titlepage.tex
Change titlepage (new format) and write Suppinfo S5 about strains

%\Sethpageshift{-8mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture horizontalement (valeur par défaut est -5.5mm)
%\Setvpageshift{0mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture verticalement (valeur par défaut est -15.5mm)

%\Universite{}    %%optionnel : à décommenter et à renseigenr si vous voulez changer le non d'université
%\Grade{}         %%optionnel : à décommenter et à renseigenr si vous voulez changer le grade
\Specialite{Biologie cellulaire}
\Arrete{7 Ao\^ut 2006}
\Auteur{Nils GIORDANO}
\Directeur{Johannes GEISELMANN}
\CoDirecteur{Hidde DE JONG}
\Laboratoire{Laboratoire Interdisciplinaire de Physique}
\EcoleDoctorale{Ecole doctorale Chimie et Science du Vivant}         
\Titre{Microbial growth control in shifting environments}
\Soustitre{Theoretical and experimental study of resource allocation in \textit{Escherichia coli}}      %%optionnel : à décommenter et à renseigenr si présence d'un sous-titre de thèse
\Depot{}

@@

\UGTRapporteur{M, Matthew SCOTT}{Associate Professor, Department of Applied Mathematics, University of Waterloo (CA)}      %% 1er rapporteur
\UGTRapporteur{M, Guy-Bart STAN}{Reader, Department of Bioengineering, Imperial College London (U.K.)}      %% second rapporteur

\UGTExaminateur{M, Olivier BERNARD}{Directeur de recherche, Inria, Nice -- Sophia-Antipolis}     %% 2ème examinateur
\UGTExaminateur{M, Matthieu JULES}{Chargé de recherche, Inra, Grignon}     %% 1er examinateur
\UGTExaminatrice{Mme, Irina MIHALCESCU}{Professeur, Université Grenoble Alpes, LIPhy}    %% 3ème examinateur

\noindent\hfil\rule{4cm}{0.1pt}\hfil

\vspace{0.3cm}

\UGTDirecteur{M, Johannes GEISELMANN}{Professeur, Université Grenoble Alpes, LIPhy}       %% Directeur de thèse
\UGTCoDirecteur{M, Hidde DE JONG}{Directeur de recherche, Inria, Grenoble -- Rhône-Alpes}     %% Co-Directeur de thèse s'il y en a
\UGTInvite{M, Jean-Luc GOUZÉ}{Directeur de recherche, Inria, Nice -- Sophia-Antipolis}
%\UGTInvitee{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}
}

\MakeUGthesePDG    %% très important pour générer la couverture de thèse

>>>>

%\Sethpageshift{???mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture horizontalement (valeur par défaut est -5.5mm)
%\Setvpageshift{???mm}   %%optionnel : à décommenter si besoin pour ajout d'espace afin de center la couvérture verticalement (valeur par défaut est -15.5mm)

%\Universite{}    %%optionnel : à décommenter et à renseigenr si vous voulez changer le non d'université
%\Grade{}         %%optionnel : à décommenter et à renseigenr si vous voulez changer le grade
\Specialite{Biologie cellulaire}
\Arrete{25 mai 2016} % ATTENTION, A VERIFIER CHAQUE ANNEE
\Auteur{Nils GIORDANO}
\Directeur{Johannes GEISELMANN}
\CoDirecteur{Hidde DE JONG}
\Laboratoire{Laboratoire Interdisciplinaire de Physique}
\EcoleDoctorale{Ecole doctorale Chimie et Science du Vivant}  
\Titre{Microbial growth control in shifting environments}
\Soustitre{Theoretical and experimental study of resource allocation in \textit{Escherichia coli}}      %%optionnel : à décommenter et à renseigenr si présence d'un sous-titre de thèse
\Depot{ (fin Mars)} %% DATE DE LA SOUTENANCE

@@

\UGTRapporteur{M, Matthew SCOTT}{Assoc. Prof.}{University of Waterloo}      %% 1er rapporteur
\UGTRapporteur{M, Guy-Bart STAN}{Reader}{Imperial College London}      %% second rapporteur

\UGTExaminateur{M, Olivier BERNARD}{DR}{Inria, Nice}     %% 2ème examinateur
\UGTExaminateur{M, Matthieu JULES}{CR}{Inra, Grignon}     %% 1er examinateur
\UGTExaminatrice{Mme, Irina MIHALCESCU}{Prof.}{Univ. Grenoble Alpes}    %% 3ème examinateur

%\noindent\hfil\rule{4cm}{0.1pt}\hfil
%
%\vspace{0.3cm}

\UGTDirecteur{M, Johannes GEISELMANN}{Prof.}{Univ. Grenoble Alpes}       %% Directeur de thèse
\UGTCoDirecteur{M, Hidde DE JONG}{DR}{Inria, Grenoble}     %% Co-Directeur de thèse s'il y en a
\UGTInvite{M, Jean-Luc GOUZÉ}{DR}{Inria, Nice}
%\UGTInvitee{...Civilité, Prénom-et-Nom...}{...titre-et-affiliation...}
}

\MakeUGthesePDG    %% très important pour générer la couvérture de thèse
